\section{Our Marketing Strategy}
\begin{enumerate}
    \item \textbf{Targeted Audience :}  age 12 - any age
    \item \textbf{An App Preview Video : }  It will help to demonstrate our app’s features, functionality and UI. Instead of just screenshots, we
    will add an app preview video to our Play Store page. It’s a great marketing strategy to engage users browsing the Play Store, and help them learn more about our app.We can easily show it on our landing page, in a Facebook ad, or on YouTube as well.
    \item \textbf{Local Media : } It is more cost-effective to reach a local audience. Reach, exposure and real-world engagement is all we need right now. We will Build a genuine connection, and care about helping people in our local community. It will land us more eyeballs, an interview, or engagement from the people we seek to serve.
    \item \textbf{Optimize App  : } For Google Play Store,We have used well-researched keywords in the application name, and we will strategically place throughout our listing, so we show up when users search for those words.It will improve our app visibility and drive downloads well, because they come up at the exact moment the customer is searching for an app like ours. It’s perfect timing.
     \item \textbf{Feedback and Reviews : } More than 60 percent of users check out an app’s rating before installing the app. And users are more likely to write a review after a negative experience in the app.We will notify users of our feedback form, so they’ll know how to contact us before they run into issues.
\end{enumerate}

